Artistic Curve Steganography Carried by Musical Audio

### 2022-11-12 writeup/paper.tex
Fixing mistake in turk figure

The effect of $\ell$ is to smooth out the noisy time series at each row $k$ of the magnitude spectrogram so that the rows in the SW-STFT match smoother transitions in the target curves.  The resulting time series $\text{SWS}_{\ell}\left({M_k}\right)$ has $N-\ell+1$ samples.  Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.  We seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.  To that end, we minimize the following objective function, one coordinate dimension $i = 1, ... d$ at a time:

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
  \caption{A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive mp3 encoding, but an $\ell$ that's too large can over-smooth.}
  \label{fig:WindowEffect}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
  \caption{A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
  \label{fig:LambdaEffect}
\end{figure}

@@

\subsubsection{Efficient Computation}
\label{sec:computation}
Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem.  Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.

@@

The main downside of non-overlapping windows is that they lead to fewer STFT frames.  For instance, for a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.  However, a quick thought experiment shows that this is still a reasonable data rate.  Suppose that we use a sliding window length $\ell=16$, for a total of 1277 carrier samples.  Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more conventional binary encoding scheme.  Then the total number of bits transmitted over 30 seconds is $1277 \times 8 \times 2$, or about 681 bits/second.  This number jumps to about 1022 bits/second for a 3D curve.  These numbers are on part with other recent techniques that are designed to be robust to noise (e.g. 900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).  Furthermore, our equivalent of a ``bit error'' is additive coordinate noise,and the target can still be visible with some amount of such noise.

>>>>

The effect of $\ell$ is to smooth out the noisy time series at each row $k$ of the magnitude spectrogram so that the rows in the SW-STFT match smoother transitions in the target curves.  The resulting time series $\text{SWS}_{\ell}\left({M_k}\right)$ has $N-\ell+1$ samples.  Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.  We then seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.  To that end, we minimize the following objective function, one coordinate dimension $i = 1, ... d$ at a time:

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$.  A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
  \label{fig:WindowEffect}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$.  A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
  \label{fig:LambdaEffect}
\end{figure}

@@

\subsubsection{Computational Complexity}
\label{sec:computation}
Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms for solving such systems efficiently via repeated evaluation of the linear system and its adjoint.  Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.  For example, let

\begin{equation}
  \label{eq:cumusum}
  C_{k, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
\end{equation}

then Equation~\ref{eq:objfn} can be rewritten as 
\begin{equation}
  \label{eq:objfncumusum}
  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k, j+\ell}-C_{k, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
\end{equation}

A similar trick can be used for the adjoint operator.

@@

Aside from window effects, the main downside of non-overlapping windows is that they lead to fewer STFT frames.  For instance, with a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.  However, a quick thought experiment shows that this is still a reasonable data rate.  Suppose that we use a sliding window length $\ell=16$, for a total of 1277 carrier samples.  Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more conventional binary encoding scheme.  Then the total number of bits transmitted over 30 seconds is $1277 \times 8 \times 2$, or about 681 bits/second.  This number jumps to about 1022 bits/second for a 3D curve.  These numbers are on par with other recent techniques that are designed to be robust to noise (e.g. 900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).  Furthermore, our equivalent of a ``bit error'' is additive coordinate noise, and the hidden signal degrades continuously with increased noise, rather than reaching a failure mode when a bit error is too high.
